%% Abstract (configurado para língua inglesa)
\begin{resumo}[Abstract]			% Título do Resumo (Abstract = Resumo em inglês)
\begin{otherlanguage*}{english}		% Língua do texto
The demand for Indoor Location Based Services
(LBS) is increasing over the past years as
smartphone market expands. There's a growing
interest in developing efficient and reliable
indoor positioning systems for mobile devices.
Smartphone users can get their fixed locations
according to the function of the GPS receiver.
This is the primary reason why there is a huge
demand for real-time location information of
mobile users. However, the GPS receiver is
often not effective in indoor environments due
to signal attenuation, even as the major
positioning devices have a powerful accuracy
for outdoor positioning.

Using preexisting information about the environment(magnetics, bluetooth, WiFi) among with smartphone's sensors data (compass, gyroscope, accelerator) attract more and more attention due to. This paper proposes an efficient and reliable android application prototype of indoor navagation.

\vspace{\onelineskip}
\noindent
\textbf{Key-words}: Palavras-chave em língua estrangeira.
\end{otherlanguage*}
\end{resumo}

%% Exemplo de resumo em francês
%\begin{resumo}[Résumé]
% \begin{otherlanguage*}{french}
%    Il s'agit d'un résumé en français.
% 
%   \textbf{Mots-clés}: latex. abntex. publication de textes.
% \end{otherlanguage*}
%\end{resumo}

%% Exemplo de resumo em Espanhol
%\begin{resumo}[Resumen]
% \begin{otherlanguage*}{spanish}
%   Este es el resumen en español.
%  
%   \textbf{Palabras clave}: latex. abntex. publicación de textos.
% \end{otherlanguage*}
%\end{resumo}
% ---
